Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-09-08 paper/paper.Rmd
Small wording changes to CI discussion

While we preregistered an analysis determining whether the original reported effect size is included in the 95\% confidence interval found in the replication, we instead opted for a straightforward comparison of point estimates. This choice was motivated by recent discussions of the utility and validity of interpreting confidence intervals in this manner [@morey2016], as well as discrepencies in the reporting of effect sizes across the articles we included (which made computing confidence intervals difficult in some cases).

>>>>

While we preregistered an analysis determining whether the original reported effect size is included in the 95\% confidence interval found in the replication, we instead opted for a straightforward comparison of point estimates. This choice was motivated by recent concerns that using confidence intervals in this manner may lead to misleading interpretations [@morey2016], as well as discrepencies in the authors' reporting of effect sizes across the articles we included (which made computing confidence intervals difficult in some cases).
